Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-12 eswc-2012/phdsymp.tex
just trimming
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@178 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO Here
\end{abstract}

@@

Current common practice in benchmarking SPARQL-enabled systems is to
use or synthesize a certain dataset, then formulate a number of
queries seen as representative of SPARQL use in some way. These
queries are then executed, and some characteristic of performance is
measured, for example the time it takes for the engine to return the
full result. Since there is a certain randomness in query times, this
process is repeated a number of times and an average response time is
found. The performance of different engines can then be compared,
based on these averages.

@@

In this case, we must consider the possibility that the random noise
can influence the conclusions. Whatever metric is used, it should be
treated as a \emph{stochastic variable}.

This opens new methodological possibilities, first and foremost
using well-established statistical hypothesis testing or ranking
rather than just comparing averages.

@@

% TODO here

@@

Finally, I have seen little work on the problem of rapidly changing
data, so the adaption of existing techniques to such situations may
also be an interesting problem.

>>>>

  For an objective evaluation as well as comparison of engines,
  benchmarks that exhaustively covers the parameter space is
  required. We propose an investigation into this problem using
  statistical experimental planning.
\end{abstract}

@@

Current common practice in benchmarking SPARQL-enabled systems is to
use or synthesize a certain dataset, then formulate a number of
queries seen as representative of SPARQL use in some way. These
queries are then executed, and some characteristic of performance is
measured, for example the time it takes for the engine to return the
full result. Since there is a certain randomness in query times, this
process is repeated a number of times and an average response time is
found. Different engines can be compared based on these averages.

@@

In this case, we must consider the possibility that the random noise
can influence the conclusions. Whatever metric is used, it should be
treated as a \emph{stochastic variable}.
This opens new methodological possibilities, first and foremost
using well-established statistical hypothesis testing or ranking
rather than just comparing averages.

@@

@@

Finally, I have seen little work on the problem of rapidly changing
data, so the adaption of existing techniques to such situations may
also be a interesting.
